%-------------------------------------------------------------------------------
%	Research Experience
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {University of Memphis} % Organisation
    {Memphis, TN} % Location
    {Aug. 2021-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{\textbf{Vision Based Navigation (PhD Research - Current)}}
      \begin{itemize}[label= - ]
                \item Multimodal Image Registration with UAV captured aerial imagery Using Deep Learning.
                \item Path Planning using Dynamic Movement Primitives.
        \end{itemize}   
      \item{\textbf{Computational Imaging Research Lab. (Master's Research)}}
      \begin{itemize}[label= - ]
                \item{Development of \textit{physics-guided image restoration} methods using \textit{Deep Learning} approaches in 3D microscopy.}
                \item{Implemented physics-guided method using various methods including UPIGAN (Unrolled Physics-Informed Generative Adversarial Network), leading a team of three.}
              \item{Simulation of the Optical Transfer function (OTF) for WF, Tunable SIM, and 3Wave SIM Microscopes.}
        \end{itemize}    
        \item{\textbf{Virtually Integrated Program (VIP - Continual)}}
        \begin{itemize}
              \item {Mentor undergraduate students with performing research, reading and writing papers, and learning programming languages including Python and Matlab.}
        \end{itemize}
      \end{cvitems}
    }

  \cventry
{Robotics R\&D Developer}  % Job title
    {\href{https://ir.linkedin.com/company/partdp-ai}{Part AI Research Center}} % Organisation
    {Tehran, Iran} % Location
    {Sep. 2020-Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed, and built cooperative farming quad-copters from scratch, leading a team of 4.}
            \item {Designed Flight Controller on Pixhauk Cube}
            \item {Implemented Object Detection algorithms including \textit{YOLO} and YOLO LITE on embedded systems.}
            \item {Started working with different embedded systems such as Khadas products and NVIDIA development boards.}
        \item {Designed a software architecture, providing the class diagram for flight simulation APIs.}
            \item {Wrote AI \textit{Python} APIs for Microsoft AirSim Flight Simulator.}
      \end{cvitems}
    } 
%---------------------------------------------------------
\cventry
    {Middle School Teacher}
    {National Organization for Development of Exceptional Talents}
    {Tehran, Iran}
    {July 2013 -  May 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Computer Programming:}}
          {Valuable projects completed and sent to different national and international competitions. Details are found at \href{https://sites.google.com/view/steacher/farzanegan-1-high-school/junior-programming}{https://sites.google.com/view/steacher/farzanegan-1-high-school/junior-programming}.}
        \item{\textbf{Robotics:}}
          {Taught basics of analog and digital circuits. Taught to build different circuits and robots from scratch. Using C in CodeVision AVR to program robots. Students participated in different national competitions.}
      \end{cvitems}
    }
    
  \cventry
{Research Collaborator}  % Job title
    {University of New South Whales (UNSW)} % Organisation
    {Sydney, Australia} % Location
    {Aug. 2020-June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Statistical data analysis on a genetics dataset: Applied different \textit{specificity tests} using \textit{hierarchical clustering} to obtain tissue-specific genes, and consequently, disease causative genes.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
{Lab. Instructor, Undergraduate Research Assistant, \& Teaching Assistant}
{Amirkabir University of Technology}
{AUT, Tehran, Iran}
{Jan. 2013-Aug. 2019}
{
    \begin{cvitems}
    \item{\textbf{Computational Intelligence Program (2018-19)}}
      \begin{itemize}[label= - ] % Description(s) of tasks/responsibilities
        \item{Teaching Assistant, helped students to solve \textit{MATLAB} problems of online and offline learning using \textit{Neural Networks} and \textit{Fuzzy} Logic including modeling and control of a system, classification, regression, and clustering. Graded assignments, project presentations, and reports.}
        \item{Adjusted the lesson plan for the Computational Intelligence lab. course.}
        \item{Lab Instructor, helped with the full control and modeling of a UGV using computational intelligence and full implementation of the lesson plan on the vehicle.}
      \end{itemize}
      \item{\textbf{Control of Multi-Vehicle Systems (CMVS) Laboratory (2016-19)}}
      \begin{itemize}[label= - ] % Description(s) of tasks/responsibilities
        \item{Thesis: Autonomously control a quadcopter and land it on a specific landing station using computer vision.}
          \item{Video processed with \textit{Raspberry pi} in \text{Python} and \textit{C++ } using \textit{OpenCV} and ARUCO markers.}
          \item{Designed separate PID controllers for each quadcopter's degrees of freedom.}
          \item{Connected \textit{C++} code to \textit{Matlab} and control the UAV  on \textit{Matlab}, Simulink.}
      \end{itemize}
      \item{\textbf{Parsian Robotics Center (2013-16)}}
      \begin{itemize}[label= - ] % Description(s) of tasks/responsibilities
        \item {Small Size Soccer League: Boost DC to DC converter design (Converting 16.8 v to 200 v),	Design a Two-way communication circuit using NRF module (wireless communication between 6 robots and a computer), Programming \textit{FPGA} using \textit{Verilog}, Full implementation of a microprocessor inside FPGA.}
            \item{Quadcopter: This project was considered an internship course. The goal was to convert a manually controlled quadcopter into an autonomous robot. Design a board that contains the following: Processor, Motor drivers, IMU: gyroscope, magnetometer, and accelerometer, Two-way communication using NRF module, Vision using a distance sensor, and an analog camera.}
      \end{itemize}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}


