%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Lectures and Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  
  \cventry
    {} % Organisation
    {Poster Presentations} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{S. P. Dajkhosh, C. Van, C. Preza, "Performance Evaluation of 3D Physics-Informed Channel Attention GAN using 3D Structured Illumination Microscopy Datasets", International Gordon Research Conference (GRC), 2022, June, Riverside, Maine}
        \item{S. P. Dajkhosh, C. Van, C. Preza, "Literature Review: Physics-Guided Deep Learning Methodologies in Computational Imaging", Electrical and Computer Engineering Department, University of Memphis, 8th Annual Poster Competition, 2022, Apr, Memphis, TN}
      \end{cvitems}
    }
%---------------------------------------------------------
  
  \cventry
    {} % Organisation
    {Conference Presentations} % Project
    {} % Location
    {} % Date(s)
    {
        \begin{cvitems} % Description(s) of projects
      \item{\textbf{Presenter:} S. P. Dajkhosh, O. Furxhi,  E. Jacobs, Abstract submitted "Aerial Image feature mapping using Deep Neural Networks", OPTICA, 2023, August, Boston, Massachusetts.}
      \item{\textbf{Presenter:} S. P. Dajkhosh, M. Hossain,  C. Preza, "USR: Unrolled Super-Resolution with Deep Priors for Structured Illumination Microscopy", OPTICA, 2023, August, Boston, Massachusetts.}
        \item{\textbf{Presenter:} S. P. Dajkhosh, M. Hossain, C. Preza, "Image reconstruction for structured illumination microscopy using an unrolled GAN", SPIE Conference, 2023, May, Orlando, Florida.}
        \item{A. Gimeno-Gomez, S.P. Dajkhosh, M.S.H. Younis, C.T.S. VAN, C. Preza, J.C. Barreiro-Hervas, G. Saavedra, "PERFORMANCE COMPARISON OF TUNABLE WOLLASTON-BASED AND THREE-WAVE INTERFERENCE STRUCTURED ILLUMINATION MICROSCOPES", Abstract accepted for \href{https://www.focusonmicroscopy.org/}{Focus on Microscopy}, 2023, Online.}
        \item{A. Gimeno-Gomez, C.T.S. Van, S. P. Dajkhosh, C. Preza, J. C. Barreiro-Hervas, G. Saavedra, “Structured illumination microscopy by use of a spatially incoherent source with arbitrary shape,” \href{https://www.focusonmicroscopy.org/}{Focus on Microscopy}, 2022, Online.}
        \item{\textbf{Presenter: }S. P. Dajkhosh, C. Van, C. Preza, "Knowledge-Based Deep Learning Modeling", Institute for Intelligent Systems Student Organization, Python Workshop, 2021, Oct, Memphis, TN.}
        \item{A. Zahedifard, S. P. Dajkhosh, M. Hosseinzadeh, Y. Ghanbari, M. Sarvestani, “\href{https://neural-reckoning.github.io/nmc3_provisional_schedule/abstracts/anis-zahedifard-enhancing-classification-of-autism-spectrum.html}{Enhancing classification of autism spectrum disorder using resting-state fMRI with machine learning approach and dimensionality reduction}”, Neuromatch 3.0, 2020, Oct, Online.}
      \end{cvitems}
    }

%---------------------------------------------------------

    
    \cventry
    {} % Organisation
    {Journal Publications} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{A. Gimeno-Gomez, S.P. Dajkhosh, M.S.H. Younis, C.T.S. VAN, C. Preza, J.C. Barreiro-Hervas, G. Saavedra, "Management of the axial modulation of the illumination pattern in structured illumination microscopy using an extended illumination source", Manuscript Submitted for Opt. Express, 2023, Online.}
        \item{A. Abraham, P. Qaladize, A. Solis, S.P. Dajkhosh, C.T.S. VAN, C. Preza, "Automatic Data Pre-Processing for Training Neural Networks for Image Restoration", Manuscript in the submission process for Quaesitum in late Jan 2023.}
        \item{MM. Rahimi, MM. Shirazi, S. P. Dajkhosh, A Zolanvari, M. Arfaee, H. Kazemi Khoshkijari, AH. Abbassi Fashami, A. Saeidi, and MA. Khosravi, \href{https://sites.google.com/view/steacher/amirkabir-university}{"Parsian Extended Team Description"}, 2016, International RoboCup, Leipzig, Germany}
        \item{A. Zolanvari, MM. Shirazi, S. P. Dajkhosh, AM. Naderi, M. Arfaee, M. Behbooei, H. Kazemi Khoshkijari, E. Tazimi, MM. Rahimi, and A. Saeidi Shahrivar, \href{https://sites.google.com/view/steacher/amirkabir-university}{"Parsian Team Description"}, 2015, International RoboCup, Hefei, China}
        \item{A. Saeidi, MH. Malmir, MM.  Shirazi, M.
        Behbooei, S. Boluki, M. Kazemi, S. M. Mohaimanian Pour, P. Ghanbari, S. Jamshidiha, S. P. Dajkhosh, and A. Zahedi., \href{https://sites.google.com/view/steacher/amirkabir-university}{"AUT-Parsian Team Description"}, 2014, International RoboCup, Jao Pessoa, Brazil}
      \end{cvitems}
    }
%---------------------------------------------------------

 
  \cventry
    {} % Organisation
    {Selected Projects} % Project
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{Digital Image Processing: Camera Calibration and virtual image dimension estimation using projection matrix in \textbf{Python} (\textbf{OpenCV}), (A), 2022}
            % \item{Machine Learning: Classify fake and real Amazon Product comments with \textbf{Neural Networks, Random Forest, and Logistic Regression} in \textbf{Python} \textbf{(Scikit Learn, Keras)}, (A), 2022}
            % \item{Independent Study:  Review and implement various deep learning architectures and datasets for microscopy image restoration using \textbf{Python} \textbf{(Keras, Pytorch)}. (A), 2022, Planning to submit two papers on this project}
            % \item{Neural Networks: Enhancing classification of autism spectrum disorder using resting-state fMRI with \textbf{Deep Neural Networks} in \textbf{Python (Keras)}. (A-), 2021, Planning to submit a paper on this project.}
            % \item{Professional Development: Perform a comprehensive review of the applications of the physics-guided \textbf{Deep Learning} for image restoration. Planning to submit a review paper on this project. SIM microscopy image simulation project in \textbf{MATLAB}. (A), 2021}
            % \item{Random Signals \& Noise: 2D Pink noise simulation of the statistical model in \textbf{MATLAB}. (A), 2021}
            \item{Digital Control Lab. IoT: Wireless Control of a UGV and Servo Motors of a flexible arm using \textbf{Raspberry Pi} and Wi-Fi module connected via Serial Port programmed with Arduino. (A+), 2017}
            \item{Advanced Programming FTDT GUI: Simulate FDTD Electromagnetic wave spread using \textbf{C++ and Python} with \textbf{Qt} graphics creator, 2017}
            \item{Computational Intelligence: Modeling and \textbf{Fuzzy} Control of an Autonomous Car in \textbf{MATLAB}. (A), 2016}
            \item{LabVIEW GUI: Design a student-professor user interface using a UDP protocol in \textbf{LabVIEW}. (A), 2016}
            \item{\textbf{Modeling Projects:} Modeling and position control of a servo motor. (A)\\ Modeling and 2D Control of a robot manipulator in \textbf{MATLAB}. (A+), 2016}
            \item{\textbf{Embedded Systems Projects:} Full Implementation of a CPLD using Verilog in XILINX ISE, Full implementation of an ARM Cortex M4 using C in STMCube and Keil uVision, and Full implementation of  AVR ATMega16 using C in CodeVision (Three courses all A+), 2015, 2017}
      \end{cvitems}
    }
    
\end{cventries}
